Subtle Gestures with the J!NS MEME

### 2021-08-08 Paper/paper.tex
Outline Analysis
Add more Related Work and cite properly

% Assigned to FB
\section{Related Work}
Something about subtlety \cite{10.1145/3290605.3300648}. Then something
about other research involving the J!NS MEME \cite{10.1145/3123021.3123060}.
Then something about their tool for automating personalization
\cite{10.1145/3174910.3174953}.

% Assigned to FB
\section{Analysis}
\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

>>>>

% As a reference, maybe useful later
Current smartglasses:
Smartglasses with cameras: Spectacles by Snap Inc. https://www.spectacles.com/
Smartglasses with EOG sensors: J!ns Meme by J!ns (website currently only in Japanese): https://jins-meme.com/

% Assigned to FB
\section{Related Work}
[Insert an introduction here]

\subsection{Face Interaction}
Detecting finger tapping on the body using acoustic sensing \cite{10.1145/1753326.1753394}.
Optical tracking system with infrared markers on fingers \cite{10.1145/2556288.2556984}.
Exploring touch interaction by placing electrodes around the ear \cite{10.1145/2468356.2468592}.
Exploring tooth click gestures \cite{10.1145/2935334.2935389}.
Eyelid gestures \cite{10.5555/2788890.2788938}.
Finger sensing IMUs \cite{10.1145/2858036.2858466}.
Hand sensing IMUs \cite{10.1145/2984511.2984582}.
Gesture recognition using wrist band \cite{10.1145/3274783.3274854}.
Tracking tongue movements with touch sensors \cite{10.1145/3311823.3311831}.
\subsection{Applications for Wearable Sensing}
Tracking eating episodes \cite{10.1145/3130902}.
Sensors in shoes for tracking exercises \cite{10.1145/3174910.3174938}.
Using hand gestures to control TV with wrist band \cite{10.1145/2641248.2641359}.
Jump performance analysis \cite{10.1145/2753509.2753512}.
Monitoring drinking with wrist-worn inertial sensors \cite{10.1145/3267242.3267253}.
\subsection{EOG Sensing and Subtle Interaction}
EOG attached to over-ear head phones \cite{10.1145/1125451.1125655}.
EOG attached to in-ear head phones \cite{10.1145/2493988.2494329}.
Demonstration of EOG sensors for eye-tracking \cite{10.1145/1520340.1520468}.
Commercial EOG glasses for activity recognition, passively \cite{10.1145/2638728.2638795}.
KissGlass for passively sensing context, not for deliberate subtle interactions \cite{10.1145/3384657.3384801}.
Defining subtlety \cite{10.1145/3290605.3300648}. 
Itchy Nose \cite{10.1145/3123021.3123060}.
% Should this one even be in the Related Work category or just mentioned in Analysis?
Itchy Nose tool for automating personalization \cite{10.1145/3174910.3174953}.

% Assigned to FB
\section{Analysis}
What was our workflow?

Which gestures did we choose?

How does the J!ns Meme work and how do we use it?

What data do we collect, how and why?
